---
title: "Data Summary"
author: "Marco Pena"
date: "2025-06-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r import-and-clean, message=FALSE, warning=FALSE}

library(tidyverse)

survey_data <- read_csv("results-survey714832.csv", na = c("N/A", "NA", ""))

problem_rows <- problems(survey_data)
print(problem_rows)

write_csv(problem_rows, "parsing_issues.csv")

saveRDS(survey_data, file = "crew_survey_cleaned_1.rds")
```

## Parsing Issues Analysis

The parsing issues show that there's a problem at row 2149, column 225, where the parser expected a logical value (TRUE/FALSE) but found "White" instead. This suggests that column 225 contains mixed data types.

```{r fix-parsing-issues, message=FALSE, warning=FALSE}

# First, let's examine the problematic column (225)

cat("Examining column 225 around row 2149:\n")
if(ncol(survey_data) >= 225) {
  col_225_sample <- survey_data[2145:2155, 225, drop = FALSE]
  print(col_225_sample)
  
  # Check the column name
  cat("\nColumn 225 name:", names(survey_data)[225], "\n")
  
  # Check unique values in this column to understand the data pattern
  cat("\nUnique values in column 225 (first 20):\n")
  unique_vals <- unique(survey_data[[225]])
  print(head(unique_vals, 20))
  
  # Check data types
  cat("\nColumn 225 class:", class(survey_data[[225]]), "\n")
}

# Read everything as character first, then convert
survey_data_safe <- read_csv("results-survey714832.csv", 
                            na = c("N/A", "NA", ""),
                            col_types = cols(.default = col_character()))

# Check
problem_rows_fixed <- problems(survey_data_safe)
cat("\nNumber of parsing issues after fix:", nrow(problem_rows_fixed), "\n")

if(nrow(problem_rows_fixed) == 0) {
  cat("All parsing issues resolved!\n")
} else {
  cat("Some parsing issues remain:\n")
  print(problem_rows_fixed)
}

survey_data_clean <- survey_data_safe %>%
  # Convert columns that should be logical but were read as character
  mutate(across(where(~ all(. %in% c("TRUE", "FALSE", "Yes", "No", NA), na.rm = TRUE)), 
                ~ case_when(
                  . %in% c("TRUE", "Yes") ~ TRUE,
                  . %in% c("FALSE", "No") ~ FALSE,
                  TRUE ~ NA
                ))) %>%
  # Convert numeric-looking columns back to numeric
  mutate(across(where(~ {
    non_na_vals <- .x[!is.na(.x)]
    length(non_na_vals) > 0 && all(str_detect(non_na_vals, "^\\d+$|^\\d*\\.\\d+$"))
  }), ~ as.numeric(.)))

cat("\nData successfully cleaned and typed!\n")
cat("Original dimensions:", dim(survey_data), "\n")
cat("Cleaned dimensions:", dim(survey_data_clean), "\n")

# Save the properly cleaned data
saveRDS(survey_data_clean, file = "crew_survey_cleaned_fixed.rds")

cat("Cleaned data saved as 'crew_survey_cleaned_fixed.rds'\n")
```

## Summary

The main parsing issue was caused by mixed data types in column 225, where the CSV parser expected logical values but encountered text values like "White". 
