---
title: "Age Distribution Analysis with Collapsed Age Groups"
subtitle: "Updated Analysis with 5 Age Brackets"
author: "Marco Pena"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: flatly
    highlight: tango
    toc: true
    toc_float: 
      collapsed: false
      smooth_scroll: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, 
  warning = FALSE, 
  message = FALSE,
  fig.width = 12, 
  fig.height = 8,
  dpi = 300,
  out.width = "100%"
)

library(dplyr)
library(ggplot2)
library(knitr)
library(kableExtra)
library(scales)
library(tidyr)
```

```{r load-data}
data_2020 <- read.csv("2020.csv")
data_2025 <- read.csv("crew_datset_keys_analysis_ready.csv")

collapse_age_groups <- function(age_col) {
  case_when(
    age_col %in% c("Under 25", "25-29") ~ "Under 30",
    age_col %in% c("30-34", "35-39") ~ "30-39", 
    age_col %in% c("40-44", "45-49") ~ "40-49",
    age_col %in% c("50-54", "55-59") ~ "50-59",
    age_col %in% c("60-64", "65 or older") ~ "60+",
    TRUE ~ as.character(age_col)
  )
}

collapsed_age_order <- c("Under 30", "30-39", "40-49", "50-59", "60+")

standardize_gender <- function(gender_col) {
  gender_col <- tolower(trimws(gender_col))
  case_when(
    gender_col %in% c("female", "woman") ~ "Women",
    gender_col %in% c("male", "man") ~ "Men",
    grepl("nonbinary|non-binary", gender_col) ~ "Nonbinary",
    TRUE ~ as.character(gender_col)
  )
}

df_2020 <- data_2020 %>%
  select(gender = m27, age = m25) %>%
  filter(!is.na(gender) & !is.na(age) & gender != "") %>%
  mutate(
    gender = standardize_gender(gender),
    age = factor(collapse_age_groups(age), levels = collapsed_age_order),
    year = 2020
  )

df_2025 <- data_2025 %>%
  select(gender = m27, age = m25) %>%
  filter(!is.na(gender) & !is.na(age) & gender != "") %>%
  mutate(
    gender = standardize_gender(gender),
    age = factor(collapse_age_groups(age), levels = collapsed_age_order),
    year = 2025
  )

gender_colors <- c("Women" = "#e74c3c", "Men" = "#3498db", "Nonbinary" = "#9b59b6")
```

# Age Group Consolidation Summary

**Original Age Groups (10):** Under 25, 25-29, 30-34, 35-39, 40-44, 45-49, 50-54, 55-59, 60-64, 65 or older

**New Age Groups (5):**
- **Under 30** (combines Under 25 + 25-29)
- **30-39** (combines 30-34 + 35-39)
- **40-49** (combines 40-44 + 45-49)
- **50-59** (combines 50-54 + 55-59)
- **60+** (combines 60-64 + 65 or older)

```{r sample-sizes}
cat("=== Sample Sizes with Collapsed Age Groups ===\n")
cat("2020 Dataset by Age:\n")
print(table(df_2020$age))
cat("\n2025 Dataset by Age:\n") 
print(table(df_2025$age))

table_2020_new <- table(df_2020$age, df_2020$gender)
table_2025_new <- table(df_2025$age, df_2025$gender)

cat("\n=== 2020 Age-Gender Cross-tabulation (Collapsed Groups) ===\n")
print(table_2020_new)
cat("\n=== 2025 Age-Gender Cross-tabulation (Collapsed Groups) ===\n")
print(table_2025_new)
```

```{r weighting-calculations}
prop_2020 <- prop.table(table_2020_new)
prop_2025 <- prop.table(table_2025_new)

all_ages <- union(rownames(prop_2020), rownames(prop_2025))
all_genders <- union(colnames(prop_2020), colnames(prop_2025))

prop_2020_expanded <- matrix(0, nrow = length(all_ages), ncol = length(all_genders),
                            dimnames = list(all_ages, all_genders))
prop_2025_expanded <- matrix(0, nrow = length(all_ages), ncol = length(all_genders),
                            dimnames = list(all_ages, all_genders))

for(age in rownames(prop_2020)) {
  for(gender in colnames(prop_2020)) {
    prop_2020_expanded[age, gender] <- prop_2020[age, gender]
  }
}

for(age in rownames(prop_2025)) {
  for(gender in colnames(prop_2025)) {
    prop_2025_expanded[age, gender] <- prop_2025[age, gender]
  }
}

weight_matrix <- prop_2020_expanded / prop_2025_expanded
weight_matrix[is.infinite(weight_matrix)] <- 0
weight_matrix[is.na(weight_matrix)] <- 0
weight_matrix[prop_2025_expanded == 0] <- 0

df_2025_weighted <- df_2025 %>%
  mutate(
    age_char = as.character(age),
    gender_char = as.character(gender)
  ) %>%
  rowwise() %>%
  mutate(
    weight = ifelse(
      age_char %in% rownames(weight_matrix) & gender_char %in% colnames(weight_matrix),
      weight_matrix[age_char, gender_char],
      0
    )
  ) %>%
  ungroup() %>%
  select(-age_char, -gender_char) %>%
  filter(weight > 0)

plot_data_2020 <- df_2020 %>%
  count(age, gender) %>%
  mutate(dataset = "2020 Original", 
         proportion = n / sum(n),
         percentage = proportion * 100)

plot_data_unweighted <- df_2025 %>%
  count(age, gender) %>%
  mutate(dataset = "2025 Unweighted", 
         proportion = n / sum(n),
         percentage = proportion * 100)

plot_data_weighted <- df_2025_weighted %>%
  count(age, gender, wt = weight) %>%
  mutate(dataset = "2025 Weighted", 
         proportion = n / sum(n),
         percentage = proportion * 100)

all_plot_data <- bind_rows(plot_data_2020, plot_data_unweighted, plot_data_weighted) %>%
  mutate(dataset = factor(dataset, levels = c("2020 Original", "2025 Unweighted", "2025 Weighted")))

comparison_2020_vs_2025 <- plot_data_2020 %>%
  select(age, gender, pct_2020 = percentage) %>%
  left_join(
    plot_data_unweighted %>% select(age, gender, pct_2025_unweighted = percentage),
    by = c("age", "gender")
  ) %>%
  mutate(
    pct_2025_unweighted = ifelse(is.na(pct_2025_unweighted), 0, pct_2025_unweighted),
    difference_unweighted = pct_2025_unweighted - pct_2020,
    abs_difference = abs(difference_unweighted)
  )

total_absolute_change <- sum(comparison_2020_vs_2025$abs_difference, na.rm = TRUE)
max_change <- max(comparison_2020_vs_2025$abs_difference, na.rm = TRUE)
```

# Age Distribution Visualizations

## Chart 1: Age-Gender Distribution Comparison (All Datasets)

```{r chart1, fig.cap="Age-Gender Distribution with Collapsed Age Groups"}
chart1 <- ggplot(all_plot_data, aes(x = age, y = percentage, fill = gender)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.8) +
  facet_wrap(~dataset, ncol = 1, scales = "free_y") +
  scale_fill_manual(values = gender_colors) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 11),
    strip.text = element_text(size = 13, face = "bold"),
    legend.position = "bottom",
    panel.grid.minor = element_blank(),
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(size = 12, hjust = 0.5, color = "gray50")
  ) +
  labs(
    title = "Age-Gender Distribution Comparison (Collapsed Age Groups)",
    subtitle = "5 Age brackets: Under 30, 30-39, 40-49, 50-59, 60+",
    x = "Age Group", 
    y = "Percentage (%)", 
    fill = "Gender"
  )

print(chart1)
```

## Chart 2: Age Distribution Trends Across Datasets

```{r chart2, fig.cap="Age Distribution Trends with Collapsed Groups"}
age_summary <- all_plot_data %>%
  group_by(dataset, age) %>%
  summarise(total_percentage = sum(percentage), .groups = "drop")

chart2 <- ggplot(age_summary, aes(x = age, y = total_percentage, color = dataset, group = dataset)) +
  geom_line(size = 1.5, alpha = 0.8) +
  geom_point(size = 4, alpha = 0.8) +
  scale_color_manual(values = c("#2c3e50", "#e67e22", "#27ae60")) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 11),
    legend.position = "bottom",
    panel.grid.minor = element_blank(),
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(size = 12, hjust = 0.5, color = "gray50")
  ) +
  labs(
    title = "Age Distribution Trends (Collapsed Groups)",
    subtitle = "Overall age composition across datasets",
    x = "Age Group", 
    y = "Percentage (%)", 
    color = "Dataset"
  ) +
  geom_text(aes(label = paste0(round(total_percentage, 1), "%")), 
            vjust = -0.5, size = 3, show.legend = FALSE)

print(chart2)
```

## Chart 3: Demographic Shift Analysis (2025 vs 2020)

```{r chart3, fig.cap="Demographic Changes with Collapsed Age Groups"}
chart3 <- ggplot(comparison_2020_vs_2025, aes(x = age, y = difference_unweighted, fill = gender)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.8) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black", size = 1) +
  scale_fill_manual(values = gender_colors) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 11),
    legend.position = "bottom",
    panel.grid.minor = element_blank(),
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(size = 12, hjust = 0.5, color = "gray50")
  ) +
  labs(
    title = "Demographic Shift Analysis: 2025 vs 2020 (Collapsed Groups)",
    subtitle = "Positive values indicate higher representation in 2025",
    x = "Age Group", 
    y = "Percentage Point Difference (2025 - 2020)", 
    fill = "Gender"
  ) +
  geom_text(aes(label = paste0(ifelse(difference_unweighted >= 0, "+", ""), 
                               round(difference_unweighted, 1))), 
            position = position_dodge(width = 0.9), 
            vjust = ifelse(comparison_2020_vs_2025$difference_unweighted >= 0, -0.3, 1.3), 
            size = 3)

print(chart3)
```

## Chart 4: Impact of Weighting on 2025 Distribution

```{r chart4, fig.cap="Effect of Weighting with Collapsed Age Groups"}
diff_data <- plot_data_weighted %>%
  select(age, gender, weighted_pct = percentage) %>%
  left_join(
    plot_data_unweighted %>% select(age, gender, unweighted_pct = percentage),
    by = c("age", "gender")
  ) %>%
  mutate(difference = weighted_pct - unweighted_pct)

chart4 <- ggplot(diff_data, aes(x = age, y = difference, fill = gender)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.8) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black", size = 1) +
  scale_fill_manual(values = gender_colors) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 11),
    legend.position = "bottom",
    panel.grid.minor = element_blank(),
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(size = 12, hjust = 0.5, color = "gray50")
  ) +
  labs(
    title = "Impact of Weighting on 2025 Data (Collapsed Groups)",
    subtitle = "Difference between weighted and unweighted 2025 distributions",
    x = "Age Group", 
    y = "Percentage Point Difference", 
    fill = "Gender"
  ) +
  geom_text(aes(label = paste0(ifelse(difference >= 0, "+", ""), 
                               round(difference, 1))), 
            position = position_dodge(width = 0.9), 
            vjust = ifelse(diff_data$difference >= 0, -0.3, 1.3), 
            size = 3)

print(chart4)
```

## Chart 5: Sample Size Comparison (Before vs After Collapse)

```{r chart5, fig.cap="Sample Size Improvement from Age Group Consolidation", fig.width=10, fig.height=6}
original_age_order <- c("Under 25", "25-29", "30-34", "35-39", "40-44", "45-49",
                       "50-54", "55-59", "60-64", "65 or older")

df_2025_original <- data_2025 %>%
  select(gender = m27, age = m25) %>%
  filter(!is.na(gender) & !is.na(age) & gender != "") %>%
  mutate(
    gender = standardize_gender(gender),
    age = factor(age, levels = original_age_order)
  )

table_2025_original <- table(df_2025_original$age, df_2025_original$gender)

min_men_original <- min(table_2025_original[, "Men"])
min_women_original <- min(table_2025_original[, "Women"]) 
min_nonbinary_original <- min(table_2025_original[, "Nonbinary"])

min_men_collapsed <- min(table_2025_new[, "Men"])
min_women_collapsed <- min(table_2025_new[, "Women"])
min_nonbinary_collapsed <- min(table_2025_new[, "Nonbinary"])

sample_comparison <- data.frame(
  scenario = rep(c("Collapsed\n(5 groups)", "Original\n(10 groups)"), each = 3),
  gender = rep(c("Men", "Women", "Nonbinary"), 2),
  min_cell_size = c(
    min_men_collapsed,
    min_women_collapsed, 
    min_nonbinary_collapsed,
    min_men_original,
    min_women_original,
    min_nonbinary_original
  )
)

sample_comparison$scenario <- factor(sample_comparison$scenario, 
                                   levels = c("Collapsed\n(5 groups)", "Original\n(10 groups)"))

cat("=== Minimum Cell Sizes Comparison ===\n")
cat("Collapsed (5 groups):\n")
cat("Men:", min_men_collapsed, "\n")
cat("Women:", min_women_collapsed, "\n") 
cat("Nonbinary:", min_nonbinary_collapsed, "\n")
cat("\nOriginal (10 groups):\n")
cat("Men:", min_men_original, "\n")
cat("Women:", min_women_original, "\n")
cat("Nonbinary:", min_nonbinary_original, "\n")

chart5 <- ggplot(sample_comparison, aes(x = scenario, y = min_cell_size, fill = gender)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.8, width = 0.6) +
  scale_fill_manual(values = gender_colors) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 10, hjust = 0.5),
    axis.text.y = element_text(size = 10),
    legend.position = "bottom",
    panel.grid.minor = element_blank(),
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(size = 11, hjust = 0.5, color = "gray50"),
    plot.margin = margin(20, 40, 20, 20, "pt")
  ) +
  labs(
    title = "Minimum Cell Size Improvement",
    subtitle = "Smallest sample size in any age-gender combination (higher is better)",
    x = "Age Group Scenario", 
    y = "Minimum Cell Size", 
    fill = "Gender"
  ) +
  geom_text(aes(label = min_cell_size), 
            position = position_dodge(width = 0.6), 
            vjust = -0.5, size = 3.5, fontface = "bold") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.15))) +
  coord_cartesian(clip = "off")

print(chart5)
```